Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality

### 2009-06-25 Paper/paper.tex
removed one line

The parameters of our experiment are divided between the ``real'' components of immersion, such as the field of view of the HMD, and the ``augmented'' components of immersion, such as the field of view of the simulated AR display, and the performance of the tracking sensor.  We introduce periods of sensor dropouts, where the augmented overlays disappear, to simulate the effect of dropouts in a real tracking system.  For example, such dropouts might occur with a magnetic sensor near interfering material.  Different display options are available in this case; for example we could use the last known sensor reading, or predict future values.  However, these options could have a positive or negative effect on performance, depending on the circumstances.  We determined that hiding the AR overlay during sensor dropouts has the least effect on performance.

>>>>

The parameters of our experiment are divided between the ``real'' components of immersion, such as the field of view of the HMD, and the ``augmented'' components of immersion, such as the field of view of the simulated AR display, and the performance of the tracking sensor.  We introduce periods of sensor dropouts, where the augmented overlays disappear, to simulate the effect of dropouts in a real tracking system.  For example, such dropouts might occur with a magnetic sensor near interfering material.  Different display options are available in this case; for example we could use the last known sensor reading, or predict future values.
%However, these options could have a positive or negative effect on performance, depending on the circumstances.
However, we determined that hiding the AR overlay during sensor dropouts would have the least effect on performance.
